---
title: "PollenDistributionSwiss - Quick Guide"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(PollenDistributionSwiss)
```

# Introduction

This document demonstrates the main functions of the PollenDistributionSwiss package, which helps analyze and visualize pollen distribution in Switzerland.

## 1. Get Pollen Forecast Data

First, let's get real pollen forecast data for Swiss cities:

```{r get_forecast_data}
# Get pollen data for multiple Swiss cities
cities <- c("Geneva", "Lugano", "Bern")
pollen_data <- get_pollen_for_list_cities(cities, "SwissCities.csv")

# Look at the structure of the data
print("Pollen data structure:")
str(pollen_data)
print("Pollen data:")
print(pollen_data)
```

```{r get_specific_forecast}
# Get detailed forecast for Geneva (coordinates)
geneva_forecast <- get_pollen_forecast(46.2044, 6.1432)
print("Geneva detailed forecast:")
print(geneva_forecast)
```

## 2. Data Visualization with Package Functions

Now let's use the forecast data with our plotting functions:

### Plot Most Common Pollen by Canton

```{r plot_most_canton}
# Plot the most common pollen types by canton using our data
plot_most_canton(pollen_data)
```

### Compare Pollen Levels Between Cities

```{r compare_cities}
# Compare pollen levels between Geneva and Lugano using coordinates
geneva_lat <- 46.2044
geneva_lon <- 6.1432
lugano_lat <- 46.0037
lugano_lon <- 8.9511

comparison_result <- compare_pollen_levels("Geneva", "Lugano", 
                                         geneva_lat, geneva_lon, 
                                         lugano_lat, lugano_lon)
print(comparison_result)
```

## 3. Data Analysis Summary

```{r data_summary}
# Summary of pollen levels by city
print("Pollen levels summary:")
if(nrow(pollen_data) > 0) {
  print(paste("Cities analyzed:", paste(pollen_data$city, collapse = ", ")))
  print(paste("Average grass pollen:", round(mean(pollen_data$grass_pollin, na.rm = TRUE), 2)))
  print(paste("Average tree pollen:", round(mean(pollen_data$tree_pollin, na.rm = TRUE), 2)))
  
  # Find city with highest grass pollen
  max_grass_city <- pollen_data$city[which.max(pollen_data$grass_pollin)]
  print(paste("City with highest grass pollen:", max_grass_city))
}
```

## Notes

-   All functions return real-time data from the Google Pollen API
-   Data is cached for better performance
-   Plots show current pollen distribution across Swiss cities
-   Data includes grass, tree, and weed pollen levels
