---
title: "Swiss Pollen Forecast Analysis"
author: "William Ambrosetti"
output: html_document
---

## Introduction

This R Markdown document showcases various functions related to pollen forecast analysis. The following functions are demonstrated:

- `get_pollen_forecast_with_cache()`: Fetches pollen data for a given location, caching the results for faster future requests.
- `get_pollin_for_list_cities()`: Retrieves pollen data for multiple cities and combines them into one data frame.
- `plot_specific_pollen()`: Creates a plot for a specific pollen type (e.g., tree, grass, or weed).
- `plot_most_canton()`: Visualizes which canton has the most pollen across all cities.
- `compare_pollen_levels()`: Compares the pollen levels between two cities and identifies which one has the least pollen.

## Function 1: `get_pollen_forecast_with_cache()`

### Description

This function retrieves pollen data for a specific latitude and longitude, with caching for faster future requests. The cache ensures that if the data has already been fetched recently, an API call is avoided.

```{r}
devtools::install("R/")
```

```{r get_pollen_forecast_with_cache}
# Example coordinates for Zurich
latitude <- 47.3769
longitude <- 8.5417

# Call the function
df_pollen <- get_pollen_forecast_with_cache(latitude, longitude)

# Show the result
head(df_pollen)
```

```{r get_pollin_for_list_cities}
# Example list of cities with coordinates
city_list <- data.frame(
  city_name = c("Zurich", "Geneva", "Bern"),
  latitude = c(47.3769, 46.2044, 46.9481),
  longitude = c(8.5417, 6.1432, 7.4474)
)

# Call the function
df_all_cities <- get_pollin_for_list_cities(city_list, "SwissCities.csv")

# Show the result
head(df_all_cities)
```

```{r plot_specific_pollen}
# Example pollen data frame (you can replace this with actual data)
plot_specific_pollen(df_pollen, pollen_type = "tree")
```

```{r plot_most_canton}
# Example pollen data frame
plot_most_canton(df_pollen)
```

```{r compare_pollen_levels}
# Example coordinates for two cities
city1_name <- "Zurich"
city1_lat <- 47.3769
city1_lon <- 8.5417

city2_name <- "Geneva"
city2_lat <- 46.2044
city2_lon <- 6.1432

# Call the function to compare
result <- compare_pollen_levels(city1_name, city2_name, city1_lat, city1_lon, city2_lat, city2_lon)
result
```


### Key Elements in the R Markdown:
1. **YAML Header**:
   - The header section at the top sets the title and output type (in this case, an HTML document). You can adjust this to your preference (PDF, Word, etc.).
   
2. **Function Documentation**:
   - For each function, I’ve included a **description** of what the function does, followed by an **example** that shows how to use it.
   
3. **R Code Chunks**:
   - Each example is enclosed in an R code chunk using triple backticks with `{r}`. This allows R to execute the code and show the results (data frames, plots, etc.) inline in the document.

4. **Plots and Visualizations**:
   - The `plot_specific_pollen()` and `plot_most_canton()` functions generate visualizations. These can be graphs or maps, depending on your function's implementation.

### Rendering the R Markdown:
1. **Knit the document**: Once your R Markdown file is complete, you can "knit" it by clicking the **Knit** button in RStudio, which will generate the HTML output.
   
2. **Ensure Packages**: Make sure you have installed any necessary packages (like `ggplot2`, `httr2`, `dplyr`, etc.) using `install.packages()` if needed.

### Additional Notes:
- **Function Output**: For functions like `plot_specific_pollen()` and `plot_most_canton()`, the plots will be displayed directly in the knitted output.
- **Cache Handling**: When showcasing caching in `get_pollen_forecast_with_cache()`, ensure that the cache file exists or that the function is capable of handling first-time calls.

Let me know if you need help with any specific part of this, or if you'd like me to refine any sections further!
