---
title: "PollenDistributionSwiss - Quick Guide"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(PollenDistributionSwiss)
```

# Introduction

This vignette demonstrates the main functions of the PollenDistributionSwiss package, which helps analyze and visualize pollen distribution in Switzerland.

## 1. Data Collection

First, let's get pollen data for some Swiss cities:

```{r get_data}
# Get pollen data for Geneva and Lugano
cities <- c("Geneva", "Lugano")
pollen_data <- get_pollen_for_list_cities(cities)

# Look at the structure of the data
str(pollen_data)
```

## 2. Data Visualization

### Plot Most Common Pollen by Canton

```{r plot_most_canton}
# Plot the most common pollen types by canton
plot_most_canton()
```

### Plot Specific Pollen Type

```{r plot_specific}
# Plot a specific pollen type (e.g., "Birch")
plot_specific_pollen("Birch")
```

### Compare Pollen Levels Between Cities

```{r compare_cities}
# Compare pollen levels between Geneva and Lugano
compare_pollen_levels("Geneva", "Lugano")
```

### Get Pollen Forecast

```{r forecast}
# Get pollen forecast for Geneva
forecast <- get_pollen_forecast("Geneva")
print(forecast)
```

## Notes

- All functions return data in a format ready for analysis
- Plots are styled for clarity and readability
- Data caching is implemented for better performance 